Emulating the CFHTLenS Weak Lensing data: Cosmological Constraints from moments and Minkowski functionals

### 2015-04-24 Paper_minkowski/Submission/paper.tex
reverted blue to normal font

In this work, we use the publicly available CFHTLenS data, consisting
of a catalog of $\approx$4.2 million galaxies, combined with a suite
of ray-tracing simulations in 91 different cosmological models to
derive constraints on the cosmological parameters $\Omega_m$,
$\sigma_8$ and the dark energy (DE) equation of state $w$.  The
statistics we consider in this work are the Minkowski functionals
(MFs) and the low--order moments (LM) of the convergence field.
Cosmological parameter inferences from CFHTLenS have been obtained
using the 2PCF~\citep{CFHTKilbinger}, and a number of authors have
investigated the constraining power of CFHTLenS using statistics that
go beyond the usual quadratic ones. Fu et al.~\citep{CFHTFu} used
three--point correlations as an additional probe for cosmology, and
found modest ($10-20\%$) improvements over the 2PCF. \textbf{These results rely on the third order statistics systematic tests performed by Simon et al. \citep{CFHTSimon}}.

@@

Suppose that a light ray reaches the observer at an angular position
$\pmb{\theta}$ on the sky: we want to know where this light ray
originated, knowing it comes from a redshift $z_s$. To answer this
question we need to integrate equation (\ref{raytrajectory}) with the
initial condition $\pmb{\beta}(0;\pmb{\theta})=\pmb{\theta}$ up to a distance
$\chi_s=\chi(z_s)$ to obtain the source angular position
$\pmb{\beta}(\chi_s;\pmb{\theta})$. \textbf{Since light rays travel undeflected from the observer to the first lens plane, the derivative initial condition in the Cauchy problem (\ref{raytrajectory}) reads $\dot{\pmb{\beta}}(0;\pmb{\theta})=0$. We indicate the derivative of $\pmb{\beta}$ with respect to $\chi$ as $\dot{\pmb{\beta}}$.} 
%
We use our proprietary implementation Inspector Gadget~(see, e.g., \cite{KHM2010}) to solve
for the light ray trajectories based \textbf{on a discretized version of equation (\ref{raytrajectory}) that is based on the multi--lens--plane algorithm (see \citep{RayTracingHartlap} for example).
Applying random periodical shifts and rotations to the $N$--body simulation data cubes, we generate $R=1000$ pseudo--independent realizations of the lens plane system used to solve (\ref{raytrajectory}).} 
%
Once we obtain the light ray trajectories, we infer the relevant weak
lensing quantities by taking angular derivatives of the ray
deflections $A(\chi_s;\pmb{\theta}) = \partial
\pmb{\beta}(\chi_s;\pmb{\theta})/\partial\pmb{\theta}$ and performing
the usual spin decomposition to infer the convergence $\kappa$ and the
shear components $(\gamma^1,\gamma^2)$,
\begin{equation}
A(\chi_s;\pmb{\theta}) = (1-\kappa(\chi_s;\pmb{\theta}))\pmb{I} - \gamma^1(\chi_s;\pmb{\theta})\sigma^3 - \gamma^2(\chi_s;\pmb{\theta})\sigma^1
\end{equation}  
where $\pmb{I}$ is the $2\times2$ identity and $\sigma^{1,3}$ are the
first and third Pauli matrices. \textbf{We perform this procedure for each of the $R$ realizations of the lens planes and we obtain $R$ pseudo--independent realizations of the $\pmb{\gamma}$ weak lensing field.} We use these different random realizations to estimate the means \textbf{(from the \texttt{CFHTemu1} simulations)} and covariance matrices \textbf{(from the \texttt{CFHTcov} simulations)} of our descriptors. \textbf{Since the random box rotations and translations that make up the \texttt{CFHTcov} simulations are based on 50 independent $N$--body runs, we believe the covariance matrices measured from this set to be more accurate than the ones measured from the \texttt{CFHTemu1} set.}

@@

For each simulated galaxy, we assign an intrinsic ellipticity by
rotating the observed ellipticity for that galaxy by a random angle on
the sky, while conserving its magnitude $\vert\mathbf{e}\vert$. To be
consistent with the CFHTLenS analysis, we adopt the weak lensing limit
($\vert\pmb{\gamma}\vert\ll1,\kappa\ll1$), i.e.
$\mathbf{g}\approx\pmb{\gamma}$ and $\mathbf{e}\approx
\mathbf{e}_s+\pmb{\gamma}$. We also add the multiplicative shear
corrections by replacing $\pmb{\gamma}$ with $(1+m)\pmb{\gamma}$. We
note that the observed ellipticity for a particular galaxy already
contains the lensing shear by large scale structure \textbf{(LSS)}, but the random
rotation makes this contribution \textbf{at least} second order in $\kappa$ \textbf{by destropying the shape spatial correlations induced by lensing from LSS}. Consistent with the weak lensing approximation, the lensing signal from the
simulations is first order in $\kappa$ and hence the randomly rotated
observed ellipticities can be safely considered as intrinsic
ellipticities.

@@

The statistical descriptors we consider in this work are the Minkowski
Functionals (MFs) and the low--order moments (LMs) of the convergence
field. The three MFs $(V_0,V_1,V_2)$ are topological descriptors of
the convergence field $\kappa(\pmb{\theta})$, probing the area,
perimeter and genus characteristic of the $\kappa$ excursion sets
$\Sigma_{\kappa_0}$, defined as
$\Sigma_{\kappa_0}=\{\kappa>\kappa_0\}$. Following
refs.~\citep{Petri2013,MinkJan} we use the following local estimators
to measure the MFs from the $\kappa$ maps:
\begin{equation*}
\label{v0meas}
V_0(\kappa_0)=\frac{1}{A}\int_A\Theta(\kappa(\pmb{\theta})-\kappa_0)d\pmb{\theta},
\end{equation*}
\begin{equation}
\label{v1meas}
V_1(\kappa_0)=\frac{1}{4A}\int_A\delta_D(\kappa(\pmb{\theta})-\kappa_0)\sqrt{\kappa_x^2+\kappa_y^2}d\pmb{\theta},
\end{equation}
\begin{equation*}
\label{v2meas}
V_2(\kappa_0)=\frac{1}{2\pi A}\int_A\delta_D(\kappa(\pmb{\theta})-\kappa_0)\frac{2\kappa_x\kappa_y\kappa_{xy}-\kappa_x^2\kappa_{yy}-\kappa_y^2\kappa_{xx}}{\kappa_x^2+\kappa_y^2}d\pmb{\theta}.
\end{equation*}
Here $A$ is the total area of the field of view and $\kappa_{x,y}$
denotes gradients of the $\kappa$ field, which we evaluate using
finite differences. \textbf{In this notation $\Theta(x)$ is the Heaviside function}
%
\begin{equation}
\Theta(x) = 
\begin{cases}
1 \,\,\,\,\,\,\,\, x\geq0 \\ \\
0 \,\,\,\,\,\,\,\, \mathrm{otherwise}
\end{cases}
\end{equation}
%
\textbf{and $\delta_D(x)$ is the Dirac delta function.}
The first Minkowski functional, $V_0$, is
equivalent to the cumulative one--point PDF of the $\kappa$ field,
while $V_1,V_2$ are sensitive to the correlations between nearby
pixels. The one--point PDF of the $\kappa$ field, $\partial V_0$, can
be obtained by differentiation $\partial
V_0(\kappa_0)=dV_0(\kappa_0)/d\kappa_0$.

@@

\begin{equation}
\label{datalikelihood}
\begin{matrix}
\mathcal{L}_d(D_i\vert \mathbf{p}) = [(2\pi)^{N_b}\det{\mathbf{C}}]^{-1/2} e^{-\frac{1}{2}\chi^2(D_i\vert \mathbf{p})}, \\ \\
\chi^2(D_i\vert \mathbf{p}) = \mathbf{[D - M(p)]}^T\mathbf{C^{-1}[D-M(p)]}.
\end{matrix}
\end{equation} 
We assume, for simplicity, that the covariance matrix $\mathbf{C}$ in
equation~(\ref{datalikelihood}) is $\mathbf{p}$--independent and
coincides with $\mathbf{C}(\mathbf{p}_0)$. The simulated descriptors $\mathbf{M(p)}$ are
measured from an average over the $R=1000$ realizations \textbf{in the \texttt{CFHTemu1} ensemble}  
\begin{equation}
M_i(\mathbf{p}) = \frac{1}{R}\sum_{r=1}^R M_i^r .
\end{equation}
The covariance matrix 
\begin{equation}
\label{datacov}
C_{ij} = \frac{1}{R-1} \sum_{r=1}^R [M_i^r(\mathbf{p}_0)-M_i(\mathbf{p}_0)][M_j^r(\mathbf{p}_0)-M_j(\mathbf{p}_0)]
\end{equation}
is measured from the \textbf{$R=1000$} realizations \textbf{in the \texttt{CFHTcov} ensemble}.
While eq.~(\ref{datacov}) gives an unbiased estimator of the
covariance matrix, its inverse is not an unbiased estimator of
$\mathbf{C}^{-1}$ (e.g. ref.~\citep{RayTracingHartlap}). Given that in
our case $R\gg N_b$, we can safely neglect the correction factor
needed to make the estimator for $\mathbf{C}^{-1}$ unbiased.

@@

We studied the accuracy of the emulator, built with the
\texttt{CFHTemu1} simulations, by interpolating the convergence
descriptors to the fiducial parameter setting
$(\Omega_m,w,\sigma_8)=(0.26,-1.0,0.8)$ and comparing the result to
the one expected from the \texttt{CFHTcov}
simulations. Figure~\ref{emulatorAccuracy} shows that our power
spectrum emulator has a \textbf{relative error} smaller than 20\% for the lower
multipoles ($l<500$), and comparable to 1\% for the higher multipoles. The MF
emulator has a \textbf{relative error} $\lesssim$10\% for the first 30 bins (which
correspond to $\kappa$ values in $[-0.04,0.08]$) and deteriorates due
to numerical noise for the remaining 20 bins. We eliminate the
residual impact of these inaccuracies using a dimensionality reduction
framework, which we explain in the next section. Nevertheless, we do
not expect these inaccuracies to affect our
conclusions. Figure~\ref{emulatorAccuracy} demonstrates that our
emulator is able to distinguish a non--fiducial model from the
fiducial one within numerical errors.  We thus found no need to
implement a more sophisticated interpolation
scheme~\footnote{Following ref.~\citep{coyote2}, we have experimented with interpolations using a Gaussian Process, but did not find a significant improvement in \textbf{relative error} over the much simpler polynomial scheme; this is in agreement with earlier results (see for example \citep{KnoxGP})}.

@@

This section describes our main results, and is organized as follows.
We begin by showing the cosmological constraints from the CFHTLenS
data for the triplet $(\Omega_m,\sigma_8,w)$, as well as for an
alternative parameterization, $(\Omega_m,\Sigma_8,w)$, with
$\Sigma_8(\alpha)\equiv \sigma_8(\Omega_m/0.27)^\alpha$. \textbf{In the next section} we give a justification on why we fix $\alpha$ to a value of $0.55$. 
We then use our simulations to perform a robustness analysis of the parameter
confidence intervals with respect to the number of PCA components used
in the projection.
We finally study whether the constraints can be tightened by combining
different descriptors. A summary with the complete set of results,
along with the relevant Figures, is shown in Table \ref{summarytable}.

@@

We show constraints from different descriptor combinations in the
$(\Omega_m,\sigma_8)$ and $(w,\Sigma_8)$ planes in Figure
\ref{contours3combined}, and on the best-constrained parameter
$\Sigma_8$ in Figure \ref{likelihoodSi8cross}. \textbf{We also provide a tabulated version of the $\Sigma_8$ constraints ($1\sigma$) in Table \ref{Sigma8Table}}. We discuss these findings in the next section.

@@

These figures also show that the current dataset is insufficient to
constrain $w$ to a reasonable precision.
This is consistent with the previous analyses of
CFHTLenS~\citep{CFHTKilbinger,CFHTFu,Companion,CFHTMasato}.  We also
note that ref.~\citep{CFHTMasato} obtained the best-fit value of
$w\approx -2$ (but with large errors that include $w=-1$ at
1$\sigma$).  We found a similar result when using a Fisher matrix to
compute confidence levels. \textbf{Since the Fisher matrix formalism is equivalent to a linear approximation of our emulator (in which all cosmological parameter dependencies are assumed to be linear interpolations between the fiducial cosmology and its variations)}, we thus attribute this bias to the \textbf{oversimplifying} assumption of linear cosmology-parameter dependence of the descriptors.  
Although the right panel in Figure
\ref{contours3combined} shows that the moments confine $w$ to isolated
regions in parameter space, we note that $w=-1$, the value favored by other existing experiments, is excluded at the $1\sigma$
level. The $2\sigma$ contours (not shown in the figure) join, and
include $w=-1$.

@@

Finally, we studied whether the combination of different statistical
descriptors can help in tightening the cosmological constraints. We
show the effects of some of these combinations in Figures
\ref{contours3combined} and \ref{likelihoodSi8cross}. The left panel
of Figure \ref{contours3combined} shows that, although combining the
power spectrum and the moments with the Minkowski functionals helps
tighten the $(\Omega_m,\sigma_8)$ constraints, it does not help in
reducing the inherent parameter bias of the MFs. The right panel of Figure
\ref{contours3combined} shows that even with these statistics
combined, $w$ remains essentially unconstrained. \textbf{\citep{CFHTHeymansTomo} found that even weak lensing tomography alone is unable to constrain $w$ sensibly}. 
Figure \ref{likelihoodSi8cross} shows that the $\Sigma_8$ combination is
already well constrained by any of the descriptors alone, without the
need of combining different descriptors.
This further clarifies that the non--quadratic descriptors mainly help
to break degeneracies, tightening contours along the
degenerate direction.

@@

\item When studying the cosmological information contained in the
  CFHTLenS data, special attention must be paid to the effect of
  residual systematic biases. While these residual systematics are
  found to be unimportant when constraining cosmology with the power
  spectrum alone, we find that these systematics need to be corrected
  to obtain unbiased constraints on the $(\Omega_m,\sigma_8)$ doublet
  using the Minkowski functionals. \textbf{We are aware that, when trying to explain the discrepancy between weak lensing and CMB constraints using the Minkowski functionals, there might be other effects to be considered, namely non--Gaussian error correlations in the descriptors and inaccuracies of the simulations on small scales. These inaccuracies could in principle affect the excursion set reconstruction at high $\kappa_0$ thresholds. We will investigate these additional sources of error in future work.}

>>>>

In this work, we use the publicly available CFHTLenS data, consisting
of a catalog of $\approx$4.2 million galaxies, combined with a suite
of ray-tracing simulations in 91 different cosmological models to
derive constraints on the cosmological parameters $\Omega_m$,
$\sigma_8$ and the dark energy (DE) equation of state $w$.  The
statistics we consider in this work are the Minkowski functionals
(MFs) and the low--order moments (LM) of the convergence field.
Cosmological parameter inferences from CFHTLenS have been obtained
using the 2PCF~\citep{CFHTKilbinger}, and a number of authors have
investigated the constraining power of CFHTLenS using statistics that
go beyond the usual quadratic ones. Fu et al.~\citep{CFHTFu} used
three--point correlations as an additional probe for cosmology, and
found modest ($10-20\%$) improvements over the 2PCF. These results rely on the third order statistics systematic tests performed by Simon et al. \citep{CFHTSimon}.

@@

Suppose that a light ray reaches the observer at an angular position
$\pmb{\theta}$ on the sky: we want to know where this light ray
originated, knowing it comes from a redshift $z_s$. To answer this
question we need to integrate equation (\ref{raytrajectory}) with the
initial condition $\pmb{\beta}(0;\pmb{\theta})=\pmb{\theta}$ up to a distance
$\chi_s=\chi(z_s)$ to obtain the source angular position
$\pmb{\beta}(\chi_s;\pmb{\theta})$. Since light rays travel undeflected from the observer to the first lens plane, the derivative initial condition in the Cauchy problem (\ref{raytrajectory}) reads $\dot{\pmb{\beta}}(0;\pmb{\theta})=0$. We indicate the derivative of $\pmb{\beta}$ with respect to $\chi$ as $\dot{\pmb{\beta}}$. 
%
We use our proprietary implementation Inspector Gadget~(see, e.g., \cite{KHM2010}) to solve
for the light ray trajectories based on a discretized version of equation (\ref{raytrajectory}) that is based on the multi--lens--plane algorithm (see \citep{RayTracingHartlap} for example).
Applying random periodical shifts and rotations to the $N$--body simulation data cubes, we generate $R=1000$ pseudo--independent realizations of the lens plane system used to solve (\ref{raytrajectory}). 
%
Once we obtain the light ray trajectories, we infer the relevant weak
lensing quantities by taking angular derivatives of the ray
deflections $A(\chi_s;\pmb{\theta}) = \partial
\pmb{\beta}(\chi_s;\pmb{\theta})/\partial\pmb{\theta}$ and performing
the usual spin decomposition to infer the convergence $\kappa$ and the
shear components $(\gamma^1,\gamma^2)$,
\begin{equation}
A(\chi_s;\pmb{\theta}) = (1-\kappa(\chi_s;\pmb{\theta}))\pmb{I} - \gamma^1(\chi_s;\pmb{\theta})\sigma^3 - \gamma^2(\chi_s;\pmb{\theta})\sigma^1
\end{equation}  
where $\pmb{I}$ is the $2\times2$ identity and $\sigma^{1,3}$ are the
first and third Pauli matrices. We perform this procedure for each of the $R$ realizations of the lens planes and we obtain $R$ pseudo--independent realizations of the $\pmb{\gamma}$ weak lensing field. We use these different random realizations to estimate the means (from the \texttt{CFHTemu1} simulations) and covariance matrices (from the \texttt{CFHTcov} simulations) of our descriptors. Since the random box rotations and translations that make up the \texttt{CFHTcov} simulations are based on 50 independent $N$--body runs, we believe the covariance matrices measured from this set to be more accurate than the ones measured from the \texttt{CFHTemu1} set.

@@

For each simulated galaxy, we assign an intrinsic ellipticity by
rotating the observed ellipticity for that galaxy by a random angle on
the sky, while conserving its magnitude $\vert\mathbf{e}\vert$. To be
consistent with the CFHTLenS analysis, we adopt the weak lensing limit
($\vert\pmb{\gamma}\vert\ll1,\kappa\ll1$), i.e.
$\mathbf{g}\approx\pmb{\gamma}$ and $\mathbf{e}\approx
\mathbf{e}_s+\pmb{\gamma}$. We also add the multiplicative shear
corrections by replacing $\pmb{\gamma}$ with $(1+m)\pmb{\gamma}$. We
note that the observed ellipticity for a particular galaxy already
contains the lensing shear by large scale structure (LSS), but the random
rotation makes this contribution at least second order in $\kappa$ by destroying the shape spatial correlations induced by lensing from LSS. Consistent with the weak lensing approximation, the lensing signal from the
simulations is first order in $\kappa$ and hence the randomly rotated
observed ellipticities can be safely considered as intrinsic
ellipticities.

@@

The statistical descriptors we consider in this work are the Minkowski
Functionals (MFs) and the low--order moments (LMs) of the convergence
field. The three MFs $(V_0,V_1,V_2)$ are topological descriptors of
the convergence field $\kappa(\pmb{\theta})$, probing the area,
perimeter and genus characteristic of the $\kappa$ excursion sets
$\Sigma_{\kappa_0}$, defined as
$\Sigma_{\kappa_0}=\{\kappa>\kappa_0\}$. Following
refs.~\citep{Petri2013,MinkJan} we use the following local estimators
to measure the MFs from the $\kappa$ maps:
\begin{equation*}
\label{v0meas}
V_0(\kappa_0)=\frac{1}{A}\int_A\Theta(\kappa(\pmb{\theta})-\kappa_0)d\pmb{\theta},
\end{equation*}
\begin{equation}
\label{v1meas}
V_1(\kappa_0)=\frac{1}{4A}\int_A\delta_D(\kappa(\pmb{\theta})-\kappa_0)\sqrt{\kappa_x^2+\kappa_y^2}d\pmb{\theta},
\end{equation}
\begin{equation*}
\label{v2meas}
V_2(\kappa_0)=\frac{1}{2\pi A}\int_A\delta_D(\kappa(\pmb{\theta})-\kappa_0)\frac{2\kappa_x\kappa_y\kappa_{xy}-\kappa_x^2\kappa_{yy}-\kappa_y^2\kappa_{xx}}{\kappa_x^2+\kappa_y^2}d\pmb{\theta}.
\end{equation*}
Here $A$ is the total area of the field of view and $\kappa_{x,y}$
denotes gradients of the $\kappa$ field, which we evaluate using
finite differences. In this notation $\Theta(x)$ is the Heaviside function and $\delta_D(x)$ is the Dirac delta function.
The first Minkowski functional, $V_0$, is
equivalent to the cumulative one--point PDF of the $\kappa$ field,
while $V_1,V_2$ are sensitive to the correlations between nearby
pixels. The one--point PDF of the $\kappa$ field, $\partial V_0$, can
be obtained by differentiation $\partial
V_0(\kappa_0)=dV_0(\kappa_0)/d\kappa_0$.

@@

\begin{equation}
\label{datalikelihood}
\begin{matrix}
\mathcal{L}_d(D_i\vert \mathbf{p}) = [(2\pi)^{N_b}\det{\mathbf{C}}]^{-1/2} e^{-\frac{1}{2}\chi^2(D_i\vert \mathbf{p})}, \\ \\
\chi^2(D_i\vert \mathbf{p}) = \mathbf{[D - M(p)]}^T\mathbf{C^{-1}[D-M(p)]}.
\end{matrix}
\end{equation} 
We assume, for simplicity, that the covariance matrix $\mathbf{C}$ in
equation~(\ref{datalikelihood}) is $\mathbf{p}$--independent and
coincides with $\mathbf{C}(\mathbf{p}_0)$. The simulated descriptors $\mathbf{M(p)}$ are
measured from an average over the $R=1000$ realizations in the \texttt{CFHTemu1} ensemble  
\begin{equation}
M_i(\mathbf{p}) = \frac{1}{R}\sum_{r=1}^R M_i^r .
\end{equation}
The covariance matrix 
\begin{equation}
\label{datacov}
C_{ij} = \frac{1}{R-1} \sum_{r=1}^R [M_i^r(\mathbf{p}_0)-M_i(\mathbf{p}_0)][M_j^r(\mathbf{p}_0)-M_j(\mathbf{p}_0)]
\end{equation}
is measured from the  $R=1000$ realizations in the \texttt{CFHTcov} ensemble.
While eq.~(\ref{datacov}) gives an unbiased estimator of the
covariance matrix, its inverse is not an unbiased estimator of
$\mathbf{C}^{-1}$ (e.g. ref.~\citep{RayTracingHartlap}). Given that in
our case $R\gg N_b$, we can safely neglect the correction factor
needed to make the estimator for $\mathbf{C}^{-1}$ unbiased.

@@

We studied the accuracy of the emulator, built with the
\texttt{CFHTemu1} simulations, by interpolating the convergence
descriptors to the fiducial parameter setting
$(\Omega_m,w,\sigma_8)=(0.26,-1.0,0.8)$ and comparing the result to
the one expected from the \texttt{CFHTcov}
simulations. Figure~\ref{emulatorAccuracy} shows that our power
spectrum emulator has a relative error smaller than 20\% for the lower
multipoles ($l<500$), and comparable to 1\% for the higher multipoles. The MF
emulator has a relative error $\lesssim$10\% for the first 30 bins (which
correspond to $\kappa$ values in $[-0.04,0.08]$) and deteriorates due
to numerical noise for the remaining 20 bins. We eliminate the
residual impact of these inaccuracies using a dimensionality reduction
framework, which we explain in the next section. Nevertheless, we do
not expect these inaccuracies to affect our
conclusions. Figure~\ref{emulatorAccuracy} demonstrates that our
emulator is able to distinguish a non--fiducial model from the
fiducial one within numerical errors.  We thus found no need to
implement a more sophisticated interpolation
scheme~\footnote{Following ref.~\citep{coyote2}, we have experimented with interpolations using a Gaussian Process, but did not find a significant improvement in relative error over the much simpler polynomial scheme; this is in agreement with earlier results (see for example \citep{KnoxGP})}.

@@

This section describes our main results, and is organized as follows.
We begin by showing the cosmological constraints from the CFHTLenS
data for the triplet $(\Omega_m,\sigma_8,w)$, as well as for an
alternative parameterization, $(\Omega_m,\Sigma_8,w)$, with
$\Sigma_8(\alpha)\equiv \sigma_8(\Omega_m/0.27)^\alpha$. In the next section we give a justification on why we fix $\alpha$ to a value of $0.55$. 
We then use our simulations to perform a robustness analysis of the parameter
confidence intervals with respect to the number of PCA components used
in the projection.
We finally study whether the constraints can be tightened by combining
different descriptors. A summary with the complete set of results,
along with the relevant Figures, is shown in Table \ref{summarytable}.

@@

We show constraints from different descriptor combinations in the
$(\Omega_m,\sigma_8)$ and $(w,\Sigma_8)$ planes in Figure
\ref{contours3combined}, and on the best-constrained parameter
$\Sigma_8$ in Figure \ref{likelihoodSi8cross}. We also provide a tabulated version of the $\Sigma_8$ constraints ($1\sigma$) in Table \ref{Sigma8Table}. We discuss these findings in the next section.

@@

These figures also show that the current dataset is insufficient to
constrain $w$ to a reasonable precision.
This is consistent with the previous analyses of
CFHTLenS~\citep{CFHTKilbinger,CFHTFu,Companion,CFHTMasato}.  We also
note that ref.~\citep{CFHTMasato} obtained the best-fit value of
$w\approx -2$ (but with large errors that include $w=-1$ at
1$\sigma$).  We found a similar result when using a Fisher matrix to
compute confidence levels. Since the Fisher matrix formalism is equivalent to a linear approximation of our emulator (in which all cosmological parameter dependencies are assumed to be linear), we thus attribute this bias to the oversimplifying assumption of linear cosmology-parameter dependence of the descriptors.  
Although the right panel in Figure
\ref{contours3combined} shows that the moments confine $w$ to isolated
regions in parameter space, we note that $w=-1$, the value favored by other existing experiments, is excluded at the $1\sigma$
level. The $2\sigma$ contours (not shown in the figure) join, and
include $w=-1$.

@@

Finally, we studied whether the combination of different statistical
descriptors can help in tightening the cosmological constraints. We
show the effects of some of these combinations in Figures
\ref{contours3combined} and \ref{likelihoodSi8cross}. The left panel
of Figure \ref{contours3combined} shows that, although combining the
power spectrum and the moments with the Minkowski functionals helps
tighten the $(\Omega_m,\sigma_8)$ constraints, it does not help in
reducing the inherent parameter bias of the MFs. The right panel of Figure
\ref{contours3combined} shows that even with these statistics
combined, $w$ remains essentially unconstrained. \citep{CFHTHeymansTomo} found that even weak lensing tomography alone is unable to constrain $w$ sensibly. 
Figure \ref{likelihoodSi8cross} shows that the $\Sigma_8$ combination is
already well constrained by any of the descriptors alone, without the
need of combining different descriptors.
This further clarifies that the non--quadratic descriptors mainly help
to break degeneracies, tightening contours along the
degenerate direction.

@@

\item When studying the cosmological information contained in the
  CFHTLenS data, special attention must be paid to the effect of
  residual systematic biases. While these residual systematics are
  found to be unimportant when constraining cosmology with the power
  spectrum alone, we find that these systematics need to be corrected
  to obtain unbiased constraints on the $(\Omega_m,\sigma_8)$ doublet
  using the Minkowski functionals. We are aware that, when trying to explain the discrepancy between weak lensing and CMB constraints using the Minkowski functionals, there might be other effects to be considered, namely non--Gaussian error correlations in the descriptors and inaccuracies of the simulations on small scales. These inaccuracies could in principle affect the excursion set reconstruction at high $\kappa_0$ thresholds. We will investigate these additional sources of error in future work.
